\documentclass{tccv}
\usepackage[english]{babel}

\begin{document}

\part{Tran Huynh}

\section{Work experience}

\begin{eventlist}
\item [optional: what has been achieved]{June 2018 -- Now}
     {Australian Broadcasting Corporation, Sydney}
     {Automation Test Analyst}

Responsible for Manual/Automation testing for Profiles and Communities team.
\newline API automation testing for music and programs API.
\item[optional: what has been achieved]{June 2018 -- Now}
     {Australian Broadcasting Corporation, Sydney}
     {Automation Test Analyst}

Responsible for Manual/Automation testing for Profiles and Communities team.
\newline API automation testing for music and programs API.
\newline Successful delivered projects include: 
\newline Responsible for QA 150+ site for Migration from HTTP to HTTPS.
\newline Define Test strategy and execute test plans for Hottest 100 website and countdown.

\item{2012 -- 2017}
     {MobileIron, Mountain View, US}
     {Scalability Developer}

Develop Java application to simulate real mobile device
activities for scalability testing product, scale to millions
of devices.
Implement application to simulate ActiveSync request/response on IOS device and Android devices.
Analyse server performance.
\newline Build site to config test and report performance test results
 ( ExtJS, Bootstrap, VertX).
\newline Assist customer support.

\item{2010 -- 2012}
     {MobileIron, Mountain View, US}
     {QA Engineer}

Contributed to the test plan, created test cases,
  performed manual black-box functionality, browser
  compatibility, usability and regression testing
\newline Performed compatibility Platform/OS/WebServer/
\newline Browser testing on WinNT/Win2K, and MacOS.
  Installed and tested application with Apache with
  multiple versions of Internet Explorer and Chrome and Firefox.
\newline Develop automated testscripts in Java, wxRuby, AutoIT, Selenium.
\newline Implement Blackberry application and Symbian application for simulated
calls and sms other activities on device, for battery life test.

\item{2008 -- 2010}
     {MobileIron, Mountain View, US}
     {Build Release Engineer}

Managed SVN commit and SVN merge between svn branches,
  fix code merge error before build and release.
\newline Manage YUM repositories for rpm upgrade.
\newline Managed daily ISO builds and ISO deployments in CentOS box,
  daily application build for Symbian S60, S60 FP1, S60 FP2 devices.

\item{2008 -- 2010}
     {MobileIron, Mountain View, US}
     {.NET Developer}

Develop .NET application to send/receive request from
  Linux box then access Exchange 2010, Exchange 2007
  system to get users, ActiveSync devices, ActiveSync
  policies on Exchange system.

\item{April 2011 -- July 2011}
     {ETNA Software, Vietnam}
     {Manual Test}

Contributed to the test plan, created test cases, performed manual black-box testing.

\end{eventlist}

\personal
	[https://www.linkedin.com/in/ju-huynh/]
    {232 Harrow Road, Glenfield, NSW 2217}
    {+61 458 878 028}
    {duhuynh8435@gmail.com}
 

\section{Software Development Skills}

\begin{factlist}

\item{Advance}
     {Java, Javascript, Postgres, MySQL, git}

\item{Intermediate}
     {C/C++, Python, Ruby, Selenium, AWS, Bamboo}

\item{Beginner}
     {Objective-C, Swift}
\end{factlist}

\section{Education}

\begin{yearlist}

\item[Ho Chi Minh City University of Technology]{2003 - 2008}
     {Bachelor of Computer Science}
     {Ho Chi Minh City, Vietnam}

\item[VSIC]{2008}
     {ICND, MCP, Java Programming, Oracle 9i}
     {Ho Chi Minh City, Vietnam}

\end{yearlist}
%:

\begin{factlist}
\item{Vietnamese}{Native speaker}
\item{English}{Good}
\end{factlist}

\end{document}
